---
title: "Lab 01 - Hello R!"
author: "[INSERT NAME]"
date: "[INSERT DATE]"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

## Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(datasauRus)
``` 

# Exercise 1

(Type your answer to exercise #1 here. Note this exercise doesn't require any R code.) 


# Exercise 2

(The answer for this exercise is given below, but you should clean up the narrative so it only includes what you want to turn in.)

First, let's plot the data in the dino dataset  (we will cover `ggplot2` in much more depth next week):

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) + 
  geom_point()
```

Next calculate the correlation between `x` and `y` in this dataset. 

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

# Exercise 3

(Add code and narrative here as needed. Note the code chunks below are labeled with `plot-circle` and `cor-circle` to provide spaces to place the code for plotting and calculating the correlation coefficient.)

(When you have finished, delete these instructions.)

```{r plot-circle}
# Your code should go here! This is a comment, which should be deleted.
```

Some more narrative can go here.

```{r cor-circle}
# Calculate the correlation here
```

Conclude with some more narrative, if needed.

# Exercise 4

(Add a labeled code chunk and narrative here. Insert code chunks using the  "insert chunk" button (a green C with a +) and select `R`. Alternatively,  use CMD + OPTION + I (Mac) or CTRL + ALT + I (Windows).)

